CRUSE to Safe Cycling in Ireland \\\large{An Open Source Tool to Support Active Travel}

### 2023-10-10 paper.qmd
Anonymisation

Data was obtained from the Central Statistics Office (CSO) and Transport Infrastructure Ireland (TII) under license and cannot be shared publicly.
The code used to generate the results presented in this paper is available at https://github.com/cruse-bike.

@@

RL led the development of the CRUSE Tool, with input from JT, EV, HM, EB, PW, GOT, DB, and SM.
SM instigated the project and coordinated its policy impact.
PW, EB and GOT provided project management and transport engineering expertise.

>>>>

Data was obtained from the Central Statistics Office (CSO) and Transport Infrastructure Ireland (TII) under license and cannot be shared publicly.
The code used to generate the results presented in this paper is available 
<!-- at https://github.com/cruse-bike. -->
[To be added after paper is accepted.]

@@

[To be added after paper is accepted.]

<!-- RL led the development of the CRUSE Tool, with input from JT, EV, HM, EB, PW, GOT, DB, and SM.
SM instigated the project and coordinated its policy impact.
PW, EB and GOT provided project management and transport engineering expertise. -->

### 2023-10-10 paper.tex
Anonymisation

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, interior hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

Although Dublin City has made progress, there are still many parts of
the Fastest route network, and even some parts of the Balanced and
Quietest route networks, that are not cycle friendly and which have high
cycling potential. According to a recent report, 71\% of residents in
the Dublin Metropolitan Area support ``more cycle tracks along roads,
physically separated from traffic and pedestrians''.\footnote{https://www.nationaltransport.ie/wp-content/uploads/2022/05/220504-WACI22\_DublinMetropolitanArea\_v35\_DIGITAL\_v2.pdf}
The results for the Dublin area could help prioritise investment in
cycling infrastructure in the city.

>>>>

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, boxrule=0pt, breakable, interior hidden, sharp corners, enhanced, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

Although Dublin City has made progress, there are still many parts of
the Fastest route network, and even some parts of the Balanced and
Quietest route networks, that are not cycle friendly and which have high
cycling potential. According to a recent report, 71\% of residents in
the Dublin Metropolitan Area support ``more cycle tracks along roads,
physically separated from traffic and pedestrians'' \citep{walking2021}.
The results for the Dublin area could help prioritise investment in
cycling infrastructure in the city.
